Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2025-05-13 paper1_jiturra.Rmd
avance review

dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  # starts_with("class3"),
  # starts_with("digclass3"),
  # starts_with("dclass3"),
  # starts_with("homclass"),
  dclass3res_V,
  # dclass3spo_V, 
  homclass3_V_res,
  know_total,
  # socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  # religion,
  partner,
  # union,
  workst,
  WEIGHT,
  region,
  # "gini_disp"=wid_gini_disp,
  "gini_disp"=difclass,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         gini_disp=scale(gini_disp))

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
homo_V_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         # socialtrust_gc+
         dclass3res_V+
         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
         female_gc+agenum_gc+
         # age2_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         # union_gc+
         workst_gc+
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         # socialtrust_gc+
         dclass3res_V+
         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
         female_gc+agenum_gc+
         # age2_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         # union_gc+
         workst_gc+
         gini_disp +loggdppercapita +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_wstate2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         # socialtrust_gc+
         dclass3res_V+
         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
         female_gc+agenum_gc+
         # age2_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         # union_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_controls <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         # socialtrust_gc+
         dclass3res_V+
         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
         female_gc+agenum_gc+
         # age2_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         # union_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         # socialtrust_gc+
         dclass3res_V+
         # dclass3spo_V_2_gc+dclass3spo_V_3_gc+dclass3spo_V_NA_gc+
         female_gc+agenum_gc+
         # age2_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         # union_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

digclas1_macro <- list(homo_V_gini,
                       homo_V_gini_gdp,
                       homo_V_gini_gdp_wstate2,
                       homo_V_gini_full2)

>>>>

dfreg <- df1 %>% dplyr::select(
  redist,prefineq,
  egal = egal2,
  # starts_with("class3"),
  # starts_with("digclass3"),
  # starts_with("dclass3"),
  # starts_with("homclass"),
  dclass3res_V,
  # dclass3spo_V, 
  homclass3_V_res,
  know_total,
  # socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  # religion,
  partner,
  # union,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  # "gini_disp"=difclass,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         gini_disp=scale(gini_disp))

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$
homo_V_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_wstate2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_controls <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2 +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full3 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         partner_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         wstate2 +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

digclas1_macro <- list(homo_V_gini,
                       homo_V_gini_gdp,
                       homo_V_gini_gdp_wstate2,
                       homo_V_gini_full2,homo_V_gini_full3)
screenreg(digclas1_macro)
